### 2016-01-25 inputs/introduction.tex
einleitung

genotype imputation have been developed for SNP-chip data, and typically 

@@

assembled \cite{international_rice_genome_sequencing_project_map-based_2005} and
recently updated \cite{kawahara_improvement_2013}. We compared the imputation 

>>>>

genotype imputation have been applied to SNP array data, and typically 

@@

assembled in 2005 \cite{international_rice_genome_sequencing_project_map-based_2005}, and
was recently updated \cite{kawahara_improvement_2013}. We compared the imputation 
